Title

### 2022-08-11 thesis/references.tex
fix references

	%%%%%%%%%%%%%%

@@

>>>>

	%%%%%%%%%%%

@@

	%%%%%%%%%%% PHASES %%%%%%%%%%%

	\bibitem{Group2012HandbookSahni}
	I.~Ahmad and S.~Ranka, \emph{Handbook of Energy-Aware and Green
		Computing}.\hskip 1em plus 0.5em minus 0.4em\relax Chapman \& Hall/CRC, 2012.

	\bibitem{iea_2021}
	Iea, ``Data centres and data transmission networks – analysis,'' Nov 2021.
	[Online]. Available:
	\url{https://www.iea.org/reports/data-centres-and-data-transmission-networks}

	\bibitem{Corcoran2017EmergingICT}
	P.~Corcoran and A.~Andrae, ``{Emerging Trends in Electricity Consumption for
		Consumer ICT},'' no. July 2013, pp. 1--56, 2017.

	\bibitem{Mathew2012Energy-awareNetworks}
	V.~Mathew, R.~K. Sitaraman, and P.~Shenoy, ``{Energy-aware load balancing in
		content delivery networks},'' \emph{Proceedings - IEEE INFOCOM}, no.
	September 2011, pp. 954--962, 2012.

	\bibitem{Fan2007}
	X.~Fan, W.-D. Weber, and L.~A. Barr¨oso, ``{Power provisioning for a
		warehouse-sized computer},'' \emph{ACM SIGARCH Computer Architecture News},
	vol.~35, no.~2, p.~13, 2007.

	\bibitem{Barroso2007TheComputing}
	L.~A. Barroso and U.~H{\"{o}}lzle, ``{The case for energy-proportional
		computing},'' \emph{Computer}, vol.~40, no.~12, pp. 33--37, 2007.

	\bibitem{Malladi2012TowardsDRAM}
	K.~T. Malladi, F.~A. Nothaft, K.~Periyathambi, B.~C. Lee, C.~Kozyrakis, and
	M.~Horowitz, ``{Towards energy-proportional datacenter memory with mobile
		DRAM},'' \emph{Proceedings - International Symposium on Computer
		Architecture}, no. Figure 1, pp. 37--48, 2012.

	\bibitem{Rotem2012Power-managementBridge}
	E.~Rotem, A.~Naveh, A.~Ananthakrishnan, E.~Weissmann, and D.~Rajwan,
	``{Power-management architecture of the intel microarchitecture code-named
		Sandy Bridge},'' \emph{IEEE Micro}, vol.~32, no.~2, pp. 20--27, 2012.

	\bibitem{Brown2005}
	L.~Brown, R.~Moore, D.~S. Li, L.~Yu, A.~Keshavamurthy, and V.~Pallipadi,
	``{ACPI in Linux},'' \emph{Symposium A Quarterly Journal In Modern Foreign
		Literatures}, vol.~51, p.~51, 2005.

	\bibitem{Hackenberg2015}
	D.~Hackenberg, R.~Sch{\"{o}}ne, T.~Ilsche, D.~Molka, J.~Schuchart, and
	R.~Geyer, ``{An Energy Efficiency Feature Survey of the Intel Haswell
		Processor},'' \emph{Proceedings - 2015 IEEE 29th International Parallel and
		Distributed Processing Symposium Workshops, IPDPSW 2015}, pp. 896--904, 2015.

	\bibitem{CARDOSO201717}
	J.~M. Cardoso, J.~G.~F. Coutinho, and P.~C. Diniz, ``Chapter 2 -
	high-performance embedded computing,'' in \emph{Embedded Computing for High
		Performance}, J.~M. Cardoso, J.~G.~F. Coutinho, and P.~C. Diniz, Eds.\hskip
	1em plus 0.5em minus 0.4em\relax Boston: Morgan Kaufmann, 2017, pp. 17--56.
	[Online]. Available:
	\url{https://www.sciencedirect.com/science/article/pii/B9780128041895000028}

	\bibitem{Shuja2012Energy-efficientCenters}
	J.~Shuja, S.~A. Madani, K.~Bilal, K.~Hayat, S.~U. Khan, and S.~Sarwar,
	``{Energy-efficient data centers},'' \emph{Computing}, vol.~94, no.~12, pp.
	973--994, 2012.

	\bibitem{Benini2000AManagement}
	L.~Benini, A.~Bogliolo, and G.~De~Micheli, ``{A survey of design techniques for
		system-level dynamic power management},'' \emph{IEEE Transactions on Very
		Large Scale Integration (VLSI) Systems}, vol.~8, no.~3, pp. 299--316, 2000.

	\bibitem{Dayarathna2016DataSurvey}
	M.~Dayarathna, Y.~Wen, and R.~Fan, ``{Data center energy consumption modeling:
		A survey},'' \emph{IEEE Communications Surveys and Tutorials}, vol.~18,
	no.~1, pp. 732--794, 2016.

	\bibitem{Irani2007}
	S.~Irani, S.~Shukla, and R.~Gupta, ``Algorithms for power savings,'' \emph{ACM
		Transactions on Algorithms}, vol.~3, p.~41, 11 2007. [Online]. Available:
	\url{https://dl.acm.org/doi/10.1145/1290672.1290678}

	\bibitem{Poellabauer2005}
	C.~Poellabauer, L.~Singleton, and K.~Schwan, ``Feedback-based dynamic voltage
	and frequency scaling for memory-bound real-time applications,'' 2005, pp.
	234--243.

	\bibitem{Saha2012}
	S.~Saha and B.~Ravindran, ``An experimental evaluation of real-time dvfs
	scheduling algorithms.''\hskip 1em plus 0.5em minus 0.4em\relax ACM Press,
	2012, pp. 1--12. [Online]. Available:
	\url{http://dl.acm.org/citation.cfm?doid=2367589.2367604}

	\bibitem{Pietri2014}
	I.~Pietri and R.~Sakellariou, ``Energy-aware workflow scheduling using
	frequency scaling.''\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 9 2014, pp.
	104--113. [Online]. Available:
	\url{http://ieeexplore.ieee.org/document/7103444/}

	\bibitem{Mashayekhy2014}
	L.~Mashayekhy, M.~M. Nejad, D.~Grosu, D.~Lu, and W.~Shi, ``Energy-aware
	scheduling of mapreduce jobs.''\hskip 1em plus 0.5em minus 0.4em\relax
	Institute of Electrical and Electronics Engineers Inc., 9 2014, pp. 32--39.

	\bibitem{Yousefi2018}
	M.~H.~N. Yousefi and M.~Goudarzi, ``A task-based greedy scheduling algorithm
	for minimizing energy of mapreduce jobs,'' \emph{Journal of Grid Computing},
	vol.~16, pp. 535--551, 12 2018.

	\bibitem{Kessler2021}
	C.~Kessler, S.~Litzinger, and J.~Keller, ``Crown-scheduling of sets of
	parallelizable tasks for robustness and energy-elasticity on many-core
	systems with discrete dynamic voltage and frequency scaling,'' \emph{Journal
		of Systems Architecture}, vol. 115, p. 101999, 5 2021. [Online]. Available:
	\url{https://linkinghub.elsevier.com/retrieve/pii/S1383762121000175}

	\bibitem{Ajmal2021}
	M.~S. Ajmal, Z.~Iqbal, F.~Z. Khan, M.~Bilal, and R.~M. Mehmood, ``Cost-based
	energy efficient scheduling technique for dynamic voltage and frequency
	scaling system in cloud computing,'' \emph{Sustainable Energy Technologies
		and Assessments}, vol.~45, p. 101210, 6 2021. [Online]. Available:
	\url{https://linkinghub.elsevier.com/retrieve/pii/S2213138821002204}

	\bibitem{Agrawal2021}
	P.~Agrawal and S.~Rao, ``Energy-efficient scheduling: classification, bounds,
	and algorithms,'' \emph{Sādhanā}, vol.~46, p.~46, 12 2021. [Online].
	Available: \url{http://link.springer.com/10.1007/s12046-021-01564-w}

	\bibitem{Schwenkler2006IntelligentInterface}
	T.~Schwenkler, ``{Intelligent Platform Management Interface},'' pp. 169--207,
	2006.

	\bibitem{Bienia2008TheSuite}
	C.~Bienia, S.~Kumar, J.~P. Singh, and K.~Li, ``{The PARSEC benchmark suite},''
	in \emph{Proceedings of the 17th international conference on Parallel
		architectures and compilation techniques - PACT '08}, no. January.\hskip 1em
	plus 0.5em minus 0.4em\relax New York, New York, USA: ACM Press, 2008, p.~72.
	[Online]. Available:
	\url{http://portal.acm.org/citation.cfm?doid=1454115.1454128}

	\bibitem{Romano2015OpenMC:Development}
	P.~K. Romano, N.~E. Horelik, B.~R. Herman, A.~G. Nelson, B.~Forget, and
	K.~Smith, ``{OpenMC: A state-of-the-art Monte Carlo code for research and
		development},'' \emph{Annals of Nuclear Energy}, vol.~82, pp. 90--97, 8 2015.
	[Online]. Available:
	\url{https://linkinghub.elsevier.com/retrieve/pii/S030645491400379X}

	\bibitem{Dongarra1988TheExplanation}
	J.~J. Dongarra, ``{The LINPACK Benchmark: An explanation},'' in \emph{Lecture
		Notes in Computer Science (including subseries Lecture Notes in Artificial
		Intelligence and Lecture Notes in Bioinformatics)}, 1988, vol. 297 LNCS, pp.
	456--474. [Online]. Available:
	\url{http://link.springer.com/10.1007/3-540-18991-2_27}

	\bibitem{electronics11050689}
	V.~R.~G. da~Silva, A.~B.~N. da~Silva, C.~Valderrama, P.~Manneback, and
	S.~Xavier-de Souza, ``A minimally intrusive approach for automatic assessment
	of parallel performance scalability of shared-memory hpc applications,''
	\emph{Electronics}, vol.~11, no.~5, 2022. [Online]. Available:
	\url{https://www.mdpi.com/2079-9292/11/5/689}
